Hybrid Partial Least Squares Regression with Multiple Functional and Scalar Predictors

### 2025-08-13 manuscript/main.tex
Proof of Lemma \ref{lemma:composite_cross_cov}

	\subsection{Tucker's Criterion}\jongmin{notation not yet changed}
	We derive that the PLS components obtained from the first step of the proposed algorithm satisfy the Tucker's Criterion \citep{Tucker1938} extended to our scalar-on-hybrid regression model setting \eqref{eq: Hybrid functional model}. We omit $l$ in the notations and first define the cross-covariance term between the response and the functional predictors (observed versions if $l=1$ and residualized versions if $l \ge 2$): 
	\begin{equation*}
\sigma_{YX}
=
 (\sigma_{YX, 1} , \ldots, \sigma_{YX, K} )
  :=
\bigl(
\mathbb{E}
[Y_1 X_{11}]
,\ldots, 
\mathbb{E}
[Y_1  X_{1K}]
\bigr)   \in \mathcal{F}^{\otimes K},
	\end{equation*}
between the response and the scalar predictor:
\begin{equation*}
\sigma_{YZ} 
= 
(\sigma_{YZ,1}, \ldots, \sigma_{YZ,p})^\top 
:= 
\bigl(
\mathbb{E}[Y_1 Z_{11}]
,\ldots,
\mathbb{E}[Y_1 Z_{1p}]
\bigr)^\top %= E(Y\mathbf{Z})
\in \mathbb{R}^p.
\end{equation*}
Based on these definitions, we define the cross-covariance term between the response and the hybrid predictor as
\begin{equation*}
\Sigma_{YW}=(\sigma_{YX}, \sigma_{YZ}) :=  
\mathbb{E}
[ Y_1 W_1 ]
=
\bigl(
\sigma_{YX}, \sigma_{YZ}
\bigr) \in \mathcal{H}.
\end{equation*}
Based on these definitions, we introduce two cross-covariance operators.
First, $\mathcal{C}_{YW}= \mathbb{E}(W_1 \otimes_\mathcal{H} Y_1): \mathcal{H} \rightarrow \mathbb{R}$ 
maps  
  $h=(f_1, \ldots, f_K, \mathbf{v}) \in \mathcal{H}$ to a real number:
\begin{equation*}
\mathcal{C}_{YW}
\mathbf{h}
:=
\mathbb{E} 
\bigl[ 
\langle W_1, h \rangle_\mathcal{H} Y_1 
\bigr] 
= 
\langle \Sigma_{YW}, h \rangle_\mathcal{H}
=
\sum \limits_{k=1}^K \int_0^1 \sigma_{YX, k}(t) \, f_k(t) \, dt 
+ 
\sigma_{YW}^\top \mathbf{v}.
\end{equation*}
Next, $\mathcal{C}_{WY} = \mathbb{E}[Y \otimes \mathbf{W}]: \mathbb{R} \rightarrow \mathcal{H}$
maps  $d \in \mathbb{R}$ to a hybrid object in $\mathcal{H}$ as follows:
%%%%
\begin{align*}		
\mathcal{C}_{WY} d 
:= 
\mathbb{E} 
\bigl[
 \langle Y_1, d \rangle W_1 
\bigr] 
= 
\mathbb{E}
[ Y_1 W_1 d ] =  d \, \Sigma_{Y W}.
\end{align*}

	Now define a new operator $\mathcal{U} = \mathcal{C}_{WY} \circ \mathcal{C}_{YW}: \mathcal{H} \rightarrow \mathcal{H}$, which performs the following mapping:
	\begin{equation*}
		\mathcal{U} \mathbf{h} =  \mathcal{C}_{WY} ( \mathcal{C}_{YW} \mathbf{h}) 
		= \mathcal{C}_{YW} (\langle \Sigma_{YW}, \mathbf{h} \rangle_\mathcal{H}) 
		=  \Sigma_{YW} \, \langle \Sigma_{YW}, \mathbf{h} \rangle_\mathcal{H} = (\Sigma_{YW} \otimes \Sigma_{YW})\mathbf{h}.
	\end{equation*}
	In other words, $\mathcal{U} = \Sigma_{YW} \otimes \Sigma_{YW}$. The following proposition presents several important properties of $\mathcal{U}$.
	\begin{proposition} \label{Proposition: property of U}
		The operator $\mathcal{U} = \mathcal{C}_{WY} \circ \mathcal{C}_{YW}= \Sigma_{YW} \otimes \Sigma_{YW}: \mathcal{H} \rightarrow \mathcal{H}$ is positive and self-adjoint. Furthermore, if there exist finite constants $Q_1$ and $Q_2$ such that
		\begin{align}
			\max \limits_{k=1, \ldots, K} \sup \limits_{t_k \in [0,1]} \sigma_{YX}^{(k)2}(t_k) < Q_1 \quad \textnormal{and} \quad  \max_{r=1, \ldots, p} \sigma_{YZ, r}^2 < Q_2,
		\end{align}
		and if each $\sigma_{YX}^{(k)}$ ($k=1, \ldots, K)$ is uniformly continuous in a sense that for any $\epsilon > 0$, there exists $\delta_k > 0$ such that for every $t_k,t^*_k \in [0,1]$ with $|t_k - t_k^* | < \delta_k$, we have that
		\begin{equation*}
			|\sigma_{yx}^{(k)}(t_k) - \sigma_{yx}^{(k)}(t_k^*) | < \epsilon,
		\end{equation*}
		then $\mathcal{U}$ is a compact operator.
	\end{proposition}
	The proof of Proposition \ref{Proposition: property of U} is provided in Appendix \ref{section:proof:Proposition: property of U}.
	By the Hilbert-Schmidt theorem (e.g., Theorem 4.2.4 in \citealp{Hsing2015}), Proposition \ref{Proposition: property of U} guarantees the existence of a complete orthonormal system of eigenfunctions $\{\xi_{(u)}\}_{u \in \mathbb{N}}$ of $\mathcal{U}$ in $\mathcal{H}$ such that $\mathcal{U} \xi_{(u)} = \kappa_{(u)}  \xi_{(u)}$, where $\{\kappa_{(u)}\}_{u \in \mathbb{N}}$ are the corresponding sequence of eigenvalues that goes to zero as $u \rightarrow \infty$, that is, $\kappa_{(1)} \ge \kappa_{(2)} \ge \cdots \ge 0$.

@@

@@

	$\mathcal{U}$ is \textit{positive} because for every $\mathbf{h} \in \mathcal{H}$,
		\langle \mathcal{U} \mathbf{h}, \mathbf{h} \rangle_\mathcal{H} = \langle \langle \Sigma_{YW}, \mathbf{h} \rangle_{\mathcal{H}} \, \Sigma_{YW}, \mathbf{h} \rangle_\mathcal{H} = \langle \Sigma_{YW}, \mathbf{h} \rangle_\mathcal{H}^2 \ge 0.

	$\mathcal{U}$ is \textit{self-adjoint} because for any $\mathbf{h}_1, \mathbf{h}_2 \in \mathcal{H}$,
	\begin{align*}
		\langle \mathcal{U} \mathbf{h}_1, \mathbf{h}_2 \rangle_\mathcal{H}  &= \langle \langle \mathbf{h}_1, \Sigma_{YW} \rangle_\mathcal{H} \Sigma_{YW}, \mathbf{h}_2 \rangle_\mathcal{H} \\
		&= \langle \mathbf{h}_1, \Sigma_{YW} \rangle_\mathcal{H} \langle \Sigma_{YW}, \mathbf{h}_2 \rangle_\mathcal{H} \\
		&= \langle \mathbf{h}_1,  \langle \Sigma_{YW}, \mathbf{h}_2 \rangle_\mathcal{H} \Sigma_{YW} \rangle_\mathcal{H}\\ 
		&= \langle \mathbf{h}_1, \mathcal{U} \mathbf{h}_2 \rangle_\mathcal{H}.
	\end{align*}

@@

			For $l_1 < l_2$,

>>>>

	\subsection{Tucker's Criterion}\jongmin{notation not yet changed}
	We derive that the PLS components obtained from the first step of the proposed algorithm satisfy the Tucker's Criterion \citep{Tucker1938} extended to our scalar-on-hybrid regression model setting \eqref{eq: Hybrid functional model}. We omit $l$ in the notations and first define the cross-covariance term between the response and the functional predictors (observed versions if $l=1$ and residualized versions if $l \ge 2$): 
\sigma_{YX}
 (\sigma_{YX, 1} , \ldots, \sigma_{YX, K} )
\mathbb{E}
[Y_1 X_{11}]
,\ldots, 
\mathbb{E}
[Y_1  X_{1K}]
\bigr)   \in \mathcal{F}^{\otimes K},
between the response and the scalar predictor:
(\sigma_{YZ,1}, \ldots, \sigma_{YZ,p})^\top 
\mathbb{E}[Y_1 Z_{11}]
,\ldots,
\mathbb{E}[Y_1 Z_{1p}]
\bigr)^\top %= E(Y\mathbf{Z})
\in \mathbb{R}^p.
Based on these definitions, we define the cross-covariance term between the response and the hybrid predictor as
\Sigma_{YW}=(\sigma_{YX}, \sigma_{YZ}) :=  
\mathbb{E}
[ Y_1 W_1 ]
\sigma_{YX}, \sigma_{YZ}
\bigr) \in \mathcal{H}.
Based on these definitions, we introduce two cross-covariance operators.
First, $\mathcal{C}_{YW}= \mathbb{E}(W_1 \otimes_\mathcal{H} Y_1): \mathcal{H} \rightarrow \mathbb{R}$ 
maps  
  $h=(f_1, \ldots, f_K, \mathbf{v}) \in \mathcal{H}$ to a real number:
\mathcal{C}_{YW}
h
\mathbb{E} 
\bigl[ 
\langle W_1, h \rangle_\mathcal{H} Y_1 
\bigr] 
\langle \Sigma_{YW}, h \rangle_\mathcal{H}
\sum \limits_{k=1}^K \int_0^1 \sigma_{YX, k}(t) \, f_k(t) \, dt 
\sigma_{YW}^\top \mathbf{v}.
Next, $\mathcal{C}_{WY} = \mathbb{E}[Y \otimes W]: \mathbb{R} \rightarrow \mathcal{H}$
maps  $d \in \mathbb{R}$ to a hybrid object in $\mathcal{H}$ as follows:
\mathcal{C}_{WY} d 
\mathbb{E} 
\bigl[
 \langle Y_1, d \rangle W_1 
\bigr] 
\mathbb{E}
[ Y_1 W_1 d ] =  d \, \Sigma_{Y W}.
Based on these two operators, we define a positive   operator as follows:
\begin{lemma}[Composite cross-covariance operator]\label{lemma:composite_cross_cov}
Define
	$\mathcal{U} := \mathcal{C}_{WY} \circ \mathcal{C}_{YW}: \mathcal{H} \rightarrow \mathcal{H}$ as an operator which performs the following mapping:
		\mathcal{U} h 
		\mathcal{C}_{WY} ( \mathcal{C}_{YW} h) 
		\mathcal{C}_{YW} (\langle \Sigma_{YW}, h \rangle_\mathcal{H}) 
		\Sigma_{YW} \, \langle \Sigma_{YW}, h \rangle_\mathcal{H} 
		(\Sigma_{YW} \otimes \Sigma_{YW}) h.
		In other words, $\mathcal{U} = \Sigma_{YW} \otimes \Sigma_{YW}$.
	 is self-adjoint and positive-semidefinite.
\end{lemma}
The proof of Lemma \ref{lemma:composite_cross_cov} is provided in Appendix \ref{section:proof:lemma:composite_cross_cov}.
 The following proposition presents several important properties of $\mathcal{U}$.
	\begin{proposition} \label{Proposition: property of U}
	 Furthermore, if there exist finite constants $Q_1$ and $Q_2$ such that
		\begin{align}
			\max \limits_{k=1, \ldots, K} \sup \limits_{t_k \in [0,1]} \sigma_{YX}^{(k)2}(t_k) < Q_1 \quad \textnormal{and} \quad  \max_{r=1, \ldots, p} \sigma_{YZ, r}^2 < Q_2,
		\end{align}
		and if each $\sigma_{YX}^{(k)}$ ($k=1, \ldots, K)$ is uniformly continuous in a sense that for any $\epsilon > 0$, there exists $\delta_k > 0$ such that for every $t_k,t^*_k \in [0,1]$ with $|t_k - t_k^* | < \delta_k$, we have that
			|\sigma_{yx}^{(k)}(t_k) - \sigma_{yx}^{(k)}(t_k^*) | < \epsilon,
		then $\mathcal{U}$ is a compact operator.
	\end{proposition}
	The proof of Proposition \ref{Proposition: property of U} is provided in Appendix \ref{section:proof:Proposition: property of U}.
	By the Hilbert-Schmidt theorem (e.g., Theorem 4.2.4 in \citealp{Hsing2015}), Proposition \ref{Proposition: property of U} guarantees the existence of a complete orthonormal system of eigenfunctions $\{\xi_{(u)}\}_{u \in \mathbb{N}}$ of $\mathcal{U}$ in $\mathcal{H}$ such that $\mathcal{U} \xi_{(u)} = \kappa_{(u)}  \xi_{(u)}$, where $\{\kappa_{(u)}\}_{u \in \mathbb{N}}$ are the corresponding sequence of eigenvalues that goes to zero as $u \rightarrow \infty$, that is, $\kappa_{(1)} \ge \kappa_{(2)} \ge \cdots \ge 0$.

@@

\section{Proof of Lemma \ref{lemma:composite_cross_cov}}\label{section:proof:lemma:composite_cross_cov}
\begin{proof}
	The operator
$\mathcal{U}$ is \textit{self-adjoint} because for any $h_1, h_2 \in \mathcal{H}$, we have
\begin{align*}
\langle 
\mathcal{U} h_1, \, h_2 
\rangle_\mathcal{H}  
&= 
\bigl \langle 
	\langle h_1, \Sigma_{YW} \rangle_\mathcal{H} \Sigma_{YW},
	\,
	h_2
\bigr \rangle_\mathcal{H}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\\&= \langle h_1, \Sigma_{YW} \rangle_\mathcal{H} \langle \Sigma_{YW}, h_2 \rangle_\mathcal{H}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\\&= 
\bigl \langle 
h_1,
\,
 \langle \Sigma_{YW}, h_2 \rangle_\mathcal{H} \Sigma_{YW} 
\bigr \rangle_\mathcal{H}
\\ 	&= \langle h_1, \mathcal{U} h_2 \rangle_\mathcal{H}.
\end{align*}
Next, 
	$\mathcal{U}$ is \textit{positive-semidefinite} because for every $h \in \mathcal{H}$, we have
\begin{equation*}
\langle 
	\mathcal{U} h,
	\,
	h
\rangle_\mathcal{H}
=
\bigl \langle 
	\langle 
		\Sigma_{YW},\, h \rangle_{\mathcal{H}}  \Sigma_{YW}, \, h
\bigr \rangle_\mathcal{H}
	= \langle \Sigma_{YW}, \, h \rangle_\mathcal{H}^2 \ge 0.
\end{equation*}
This completes the proof of Lemma \ref{lemma:composite_cross_cov}.
\end{proof}

@@

@@

			For $l_1 < l_2$, we have
